# Homework 2

## Task 1

1. Create vectors for pretreatment data (x) and after treatment data (y)

```{r}
x <- c(120, 151, 125, 126, 115, 132, 132, 129, 134, 139, 127, 122, 127, 135, 133, 128, 147, 138, 140, 132)

y <- c(127, 145, 135, 122, 115, 122, 123, 126, 126, 129, 132, 146, 120, 114, 121, 120, 128, 120, 133, 115)
```

2. Assign names to the subjects within each vector
```{r}
names(x) <- paste("Subject", 1:20, sep = "_")

names(y) <- paste("Subject", 1:20, sep = "_")
```
```{r}
x
```
```{r}
y
```
3. Calculate the change in blood pressure for each patient and save a new vector z
```{r}
z <- (y-x)
z
```
4. Calculate the average decrease in blood pressure across all patients. 
```{r}
mean(z, trim = 0, na.rm = FALSE)
```


5. Determine which patients experienced a decrease in blood pressure after treatment (a positive change).
```{r}
which(z>0)
```


6. Subset the vector of differences to only return those that have a positive change. 
```{r}
p <- which(z>0)
```


7. Calculate the average decrease in blood pressure for those where the blood pressure decreased (positive change).
```{r}
mean(p, trim = 0, na.rm = FALSE)
```

